% LaTeX file for resume 
% This file uses the resume document class (res.cls)
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\usepackage{xcolor}
\usepackage{hyperref}

\hypersetup{
	colorlinks=true,
	linkbordercolor=,
	linkcolor=blue
}

\topmargin=-0.5in  % start text higher on the page
\setlength{\textheight}{10in} % increase text height to fit resume on 1 page
\begin{document}  
\name{VASILI SVIRIDOV}

\address{ \#304 - 6742 Station Hill Ct \\ Burnaby, BC, V3N4V2\\Canada }
                        
\begin{resume}

\section{CONTACT ME}
	\begin{ncolumn}{2}
		\href{mailto:vasili@sviridov.ca}{vasili@sviridov.ca} & +1 (604) 767 7735 \\
		\href{http://vasi.li}{http://vasi.li} & \href{http://twitter.com/vsviridov}{@vsviridov}
	\end{ncolumn}
 
\section{PROJECTS}
	\section{2011 --- 2012\\\href{http://www.rbcgam.com/gam/}{RBC GAM}}
	Was engaged in a Senior Web Development role in a small team to design, build, and support a set of frameworks, utilizing ASP.Net MVC and HTML5. Built several products with the frameworks mentioned, including a user management system, a framework for ACL, and several business applications.
	\section{2008 --- 2011\\\href{http://positrace.com}{Global Fleet Management}}
	 Designed and wrote large portions for a GPS tracking SaaS platform, including, but not limited to, fully dynamic map interface powered by Ajax and Web Sockets to display information about hundreds of vehicles in real time, using JavaScript and Google Maps API. Wrote most of the client facing forms and also a back office application for internal use by sales and support personnel. Developed a custom ORM solution based on MySQL. Wrote Node.JS backend to integrate the web site with our RabbitMQ backend, passing thousands of location and state messages per second. Wrote a mobile web site using ASP.MVC and jQuery mobile.
	\section{2006 --- 2007\\\href{https://wwwphn.com/}{Phillips,\\Hager \& North}}
	Worked as a consultant for an investment management firm, helping them to build a custom solution to provide clients with pricing and trading controls utilizing the DotNetNuke CMS.
	\section{2005 --- 2006\\\href{http://cougartg.com}{Cougar TG}}
	Worked on an e-commerce system for a Vancouver software manufacturer company. Developed visuals and business logic to perform various up-sells, cross-sells and promotions, using vanilla ASP.Net Web Forms and MS SQL Server.

\section{STACK} 
	\normalsize{\section{Languages}}
		\itemsep -2pt
 		\begin{itemize}
 			\item C\#, JavaScript, Scala, PHP
		\end{itemize}
	\normalsize{\section{Markup \& FrontEnd}}
		\itemsep -2pt
		\begin{itemize}
			\item HTML5
			\item CSS, LESS
			\item Bootstrap
			\item jQuery, jQMobile, MooTools, WebSockets
			\item WPF/Silverlight
		\end{itemize}
	\normalsize{\section{Backend}}
		\begin{itemize}
			\item IIS/Apache/Nginx
			\item CouchDB/Riak
			\item RabbitMQ
			\item Node.js
		\end{itemize}
	\normalsize{\section{DevOps}}
		\begin{itemize}
			\item GIT/SVN
			\item Trac/Indefero/Bugzilla
			\item Jenkins, CrusieControl.Net
		\end{itemize}
\newpage
\section {INTERESTS}
	\normalsize{\section{Natural Languages}}
		\begin{itemize}
			\item Japanese
			\item Esperanto
		\end{itemize}
	\normalsize{\section{Computer Languages}}
		\begin{itemize}
			\item Haskell
			\item F\#
			\item Erlang
		\end{itemize}
	\normalsize{\section{Frameworks \& Technologies}}
		\begin{itemize}
			\item FubuMVC
			\item Play Framework
		\end{itemize}



\end{resume} 
\end{document}









