\cvsection{Experience}
\begin{cventries}
  \cventry
    {CTO}
    {\href{https://charit.ee}{\faGlobe\enspace Charit.ee Inc.}}
    {Vancouver, BC}
    {Jul. 2015 - Apr. 2017}
    {
      \begin{cvitems}
        \item {Was in charge of picking the technology stack, infrastructure, and architecture}
        \item {Managed the project using various tools}
        \item {Project was mostly based on open-source technologies}
      \end{cvitems}
      \hfill\break
      \begin{cvskills}
        \cvskill {Frontend}{React, Redux, HTML5, Webpack, Babel, ES7}
        \cvskill {Backend}{PostgreSQL, Node.js, GraphQL, nginx, wal-e}
        \cvskill {CI, etc...}{GitLab, Trello, Slack, AWS}
      \end{cvskills}
    }

  \hfill\break
  \cventry
    {CTO}
    {FullRoster}
    {Vancouver, BC}
    {Jan 2015 - Jan 2016}
    {
      Building a sports tournament organization software. The solution was used by several high-profiles companies in Greater Vancouver area, but ultimately failed to get commercialized.
      \begin{cvskills}
        \cvskill {Frontend}{jQuery, HTML5, Responsive}
        \cvskill {Backend}{Ruby on Rails, PostgreSQL}
        \cvskill {Stack}{Github, Amazon Web Services}
      \end{cvskills}
    }
  \cventry
    {Web Developer}
    {\href{https://move.com}{\faGlobe\enspace Move Inc.}}
    {Richmond, BC}
    {Apr 2013 - Feb 2015}
    {
      Building a "Local" experience for \href{https://www.realtor.com/local/}{realtor.com} website. Developed a web UI to display various information about a geographical locale. Enhanced existing and wrote new custom software to automate deployment from \texttt{git checkout -b} to a live product running in test environment. Wrote a custom IRC bot to notify team members of various deployment states, pending merges, and to help orchestrate deployments across server farms and notify key stakeholders of pending downtimes.
      \begin{cvskills}
        \cvskill {Frontend}{Angular.js}
        \cvskill {Backend}{Node.js, MongoDB}
        \cvskill {Tooling} {Node.js, C\#, GitLab, Gitbot}
      \end{cvskills}
    }

  \cventry
    {IT Consultant}
    {\href{https://www.phn.com}{\faGlobe\enspace RBC GAM (Phillips, Hager, \& North)}}
    {Vancouver, BC}
    {2006 - 2007, 2011 - 2012}
    {
      Worked as a consultant for an investment management firm, helping them to build a custom solution to provide clients with pricing and trading controls utilizing the DotNetNuke CMS. Designed, built, and supported a set of frameworks, utilizing ASP.Net MVC and HTML5. Built several products with the frameworks mentioned, including a user management system, a framework for ACL, and several business applications. Heavily utilized Twitter Bootstrap, jQuery, jQueryUI frameworks along with custom JavaScript code to handle complex data entry scenarios, including Ajax validation and processing. Built a scheduler application with web interface, that allowed users to set up various data downloads from external vendors. It featured a simple to use UI and a system of notifications via email. Another application was a fund performance simulator, for which I have developed a UI, that allowed people to set up various parameters of the simulation. It featured a complex matrix of interdependent controls where changing a parameter would affect options for other controls.
    }
    
  {
    \footnotesize For additional experience please refer to my LinkedIn profile.
  }
\end{cventries}
